Damage localization based on vibrations

### 2016-12-02 slides/slides.tex
bridge
slides physical models

\begin{frame}{Bridge}
\includegraphics[width=5cm]{images/crack.jpg}
\end{frame}

@@

\begin{frame}{4 levels}
\end{frame}

@@

\begin{center}
$M \ddot{q}(t) + C \dot{q}(t) + K q(t) = f(t)$
\end{center}

@@

\begin{frame}{Continous-time state-space model}

@@

$x =
\begin{pmatrix}
\dot{q} \\
q
\end{pmatrix}$

@@

\begin{center}
$\left\{
\begin{array}{ll}
x_{k+1} & = A_dx_k + B_df_k \\
y_k & = C_dx_k + B_df_k
\end{array}
\right.$

@@

@@

\begin{frame}{Intro}

\begin{itemize}
\item FRF calcul
\item Interpolation on the FRF
\item Error calcul
\end{itemize}

@@

\begin{frame}{Interpolation}
\begin{center}
\includegraphics[width=5cm]{images/interpolation.png}
\end{center}

@@

\begin{frame}{Error}

\begin{center}
$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$

$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$

$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$

@@

\begin{frame}{Proba}
\begin{center}
\includegraphics[width=5cm]{images/gaussiennes.png}
\end{center}
\end{frame}

@@

Thus, we have the matrices of the discrete-time state-space model
\begin{center}
$\left\{
\begin{array}{ll}
x_{k+1} & = A_dx_k + B_df_k \\
y_k & = C_dx_k + B_df_k
\end{array}
\right.$
\end{center}

>>>>

\begin{frame}{Bridge}
\begin{center}
\includegraphics[width=4cm]{images/crack.jpg}

\pause

\includegraphics[width=5cm]{images/bridge.png}
\end{center}
\end{frame}

@@

\begin{frame}{4 levels}
\begin{center}
\begin{itemize}
\item Detection: Is the structure damaged or not?
\item Localization: Where is the damaged area located?
\item Quantification: What is the extent of damage?
\item Prediction: What is the remaining service life of the structure?
\end{itemize}
\end{center}
\end{frame}

@@

\begin{center}
\includegraphics[height=4cm]{images/finite_element.png}

@@

\begin{frame}{Continous-time state-space model}
With the variable change $x =
\begin{pmatrix}
\dot{q} \\
q
\end{pmatrix}$, we have:

@@

where $A_c, B_c, C_c$ and $D_c$ rely on $M, C$ and $K$.

@@

We need to convert the system to discret time:

\begin{center}

$\left\{
\begin{array}{ll}
x_{k+1} & = A_dx_k + B_df_k \\
y_k & = C_dx_k + B_df_k
\end{array}
\right.$

@@

\begin{center}

@@

\begin{frame}{FRF Interpolation Method}

\begin{alertblock}{Main hypothesis}
A concentrated damage reflects
in a loss of spatial regularity of the vibrational profile of a
structure, compared with the undamaged state.
\end{alertblock}

\underline{Main steps}:
\begin{itemize}
\item Frequency Response Function (FRF) calcul
\item Interpolation on the FRF
\item Error calcul
\end{itemize}

@@

\begin{frame}{Interpolation}
Cubic polynomial spline interpolation:

\begin{center}
\includegraphics[width=5cm]{images/interpolation.png}
\end{center}

@@

\begin{frame}{Error calcul}

For each sensor $z_l$ at the frequency $f_i$:
\begin{center}
$E(z_l,f_i) = | H_R(z_l,f_i) - H_S(z_l,f_i) |$
\end{center}

For each sensor:
\begin{center}
$E(z_l) = \sqrt{  \sum\limits_{i=1}^N  E^2(z_l,f_i) }$
\end{center}

Difference with the reference state:
\begin{center}
$\Delta E(z_l) = E_d(z_l) - E_0(z_l)$
\end{center}

@@

\begin{frame}{Probability of identification of a damage}
\begin{center}
\includegraphics[height=4cm]{images/gaussiennes.png}
\end{center}
\end{frame}

@@

Thus, we have the matrices of the discrete-time state-space model:
\begin{center}
$\left\{
\begin{array}{ll}
x_{k+1} & = A_dx_k + B_df_k \\
y_k & = C_dx_k + B_df_k
\end{array}
\right.$
\end{center}
